Paper figures

### 2021-05-12 notebooks/17-PRS_dendrogram_cluster_investigation-020921.Rmd
changed package references and added 3rules

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
#source('src/R/plot_density_prs.R')
source('src/R/get.subclusters.dendrogram.R')
library(RColorBrewer)
col =brewer.pal(n=8,name='Set1')
sensor_colors = col[1:4]
effector_colors = col[5:8]
```

# Read data
Read data in python, from pickle file saved earlier.
```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm
from src.utils import *
import scipy.cluster.hierarchy as sch

@@

# Import goatools functions from src/utils.py
utils <- import('src.utils')
create_goa = utils$create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
goea = create_goa[[1]]
geneid2name = create_goa[[2]]
#utils$query_goatools(sensors_pcc,goea,geneid2name)
eff_go_terms <- list()
sens_go_terms <- list()
for(i in 1:4){
    print(i)
    subcluster <- effector_pcc%>%filter(clusters==i)
    query <- utils$query_goatools(subcluster,goea,geneid2name)
    print(head(query))
    eff_go_terms[i] = query[1,4]
}
effector_pcc <- as.character(eff_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(effector_pcc,by=c('rowname'='clusters'))%>%rename(clusters=rowname)

>>>>

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
#source('enm/R/plot_density_prs.R')
source('enm/R/get.subclusters.dendrogram.R')
library(RColorBrewer)
col =brewer.pal(n=8,name='Set1')
sensor_colors = col[1:4]
effector_colors = col[5:8]
```

# Read data
Read data in python, from pickle file saved earlier.
```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from enm.enm import Enm
from enm.utils import *
import scipy.cluster.hierarchy as sch

@@

# Import goatools functions from enm/utils.py
utils <- import('enm.utils')
create_goa = utils$create_goea(gaf = 'data/raw/ontology/sgd.gaf', obo_fname='data/raw/ontology/go-basic.obo', background='data/interim/costanzo_gc_bg.tsv', sgd_info_tab = 'data/raw/ontology/SGD_features.tab')
goea = create_goa[[1]]
geneid2name = create_goa[[2]]
#utils$query_goatools(sensors_pcc,goea,geneid2name)
eff_go_terms <- list()
sens_go_terms <- list()
for(i in 1:4){
    print(i)
    subcluster <- effector_pcc%>%filter(clusters==i)
    query <- utils$query_goatools(subcluster,goea,geneid2name)
    print(head(query))
    eff_go_terms[i] = query[1,4]
}
effector_pcc <- as.character(eff_go_terms)%>%as.data.frame()%>%rownames_to_column()%>%mutate(rowname=as.numeric(rowname))%>%rename(cluster_go_term='.')%>%right_join(effector_pcc,by=c('rowname'='clusters'))%>%rename(clusters=rowname)

### 2021-05-12 notebooks/CSHL_plots_022621.Rmd
changed package references and added 3rules

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("src/R/plot_density_prs.R")
source("src/R/get.subclusters.dendrogram.R")
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

@@

from src.visualize.visualize import heatmap_annotated
#import src
#import importlib
#importlib.reload(src.visualize.visualize)
heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,
#                 row_colors=colors, col_colors=colors)

>>>>

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("enm/R/plot_density_prs.R")
source("enm/R/get.subclusters.dendrogram.R")
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from enm.enm import Enm

@@

from enm.visualize.visualize import heatmap_annotated
#import enm
#import importlib
#importlib.reload(enm.visualize.visualize)
heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,
#                 row_colors=colors, col_colors=colors)

### 2021-05-12 notebooks/paper_plots_0216_pcc_only_clustered.Rmd
changed package references and added 3rules

from src.visualize.visualize import heatmap_annotated
#import src
#import importlib
importlib.reload(src.visualize.visualize)
heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,
#                 row_colors=colors, col_colors=colors)

>>>>

from enm.visualize.visualize import heatmap_annotated
#import enm
#import importlib
importlib.reload(enm.visualize.visualize)
heatmap_annotated(prs_mat, prs_mat_cl_orig, figure_path=r.figure_folder, row_linkage=e_pcc.row_linkage, col_linkage=e_pcc.col_linkage, save_figure=True)#,
#                 row_colors=colors, col_colors=colors)

### 2021-05-12 notebooks/paper_plots_0909.Rmd
changed package references and added 3rules

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
source('src/R/plot_density_prs.R')
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

>>>>

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
source('enm/R/plot_density_prs.R')
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from enm.enm import Enm

### 2021-05-12 notebooks/paper_plots_1211.Rmd
changed package references and added 3rules

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
source('src/R/plot_density_prs.R')
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

>>>>

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
source('enm/R/plot_density_prs.R')
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import pickle 
import os
import re
import itertools as itr
from enm.enm import Enm

### 2021-05-12 notebooks/paper_plots_1213_pcc_only.Rmd
changed package references and added 3rules

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
setwd("../")
source("src/R/plot_density_prs.R")
figure_path = 'reports/figures/0404_paperfigure_sensors/'
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

>>>>

```{r}
library(reticulate)
# use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv("enm")
#setwd("../")
source("enm/R/plot_density_prs.R")
figure_path = 'reports/figures/0404_paperfigure_sensors/'
```

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from enm.enm import Enm

### 2021-05-12 notebooks/poster_plots_1023.Rmd
changed package references and added 3rules

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from src.enm import Enm

>>>>

```{python}
import matplotlib.pyplot as plt
import matplotlib as mpl
import networkx as nx
import numpy as np
import pandas as pd
import plotnine as p9
import pickle 
import os
import re
import itertools as itr
from enm.enm import Enm
